Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-16 paper/main.tex
Table variants

>>>>

\begin{figure}[h]
    \begin{tabular}{|r|r|r|r|r|}
        \hline
                       &\eval & \texttt{evalq} & \texttt{eval.parent} & \texttt{local} \\
       Static    sites  & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
       Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
        Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\
%        \% triggered & \Triggeredevalpercent & \Triggeredevalqpercent & \Triggeredevalparentpercent & \Triggeredlocalpercent \\
        \hline
    \end{tabular}
    \caption{Variants of \eval} \label{tab:variantseval}
\end{figure}
